|

### 2024-12-20 manuscript_tf/manuscript.Rmd
update

---
title: |
  Examining the Impact of School Closures on COVID-19 Infections in Europe and their Effects on Different Age Cohorts
author:
  - name: Damien Dupré
    affil: 1
    email: damien.dupre@dcu.ie
  - name: Edgar Morgenroth
    affil: 1
    email: edgar.morgenroth@dcu.ie
affiliation:
  - num: 1
    address: |
      Business School, Dublin City University

@@

bibliography: bibliography.bib
abstract: |
  This paper analyzes the trends of COVID-19 cases in different age groups in selected European countries, assessing to what extent school closures helped reduce case numbers, how school closures affected case numbers in different age groups, and how COVID-19 spread between age groups. The study also evaluates the effects of school closures on COVID-19 cases using a Generalized Additive Model (GAM). The findings demonstrate a decreasing non-linear effect of school closure on the total COVID-19 case number across all countries studied. However, the analysis of age groups only reveals a consistent downward trend in infections in the 0 to 4 pre-school age group, while the school-going age groups 5 to 14 exhibit a significant increase in cases. Age groups 15 to 24 show a surge immediately after closure, followed by a decline. Transfer Entropy calculations highlight asymmetry in age group influences, indicating that changes in COVID-19 cases in certain age groups predict changes in other age groups but not vice versa. These findings contribute to a better understanding of COVID-19 dynamics in European countries and provide insights for public health strategies and interventions.
keywords: |
  COVID-19; School Closures; Intergenerational Transmission.
output:
  bookdown::pdf_book:
    base_format: rticles::tf_article
    keep_tex: false
header-includes:
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{threeparttable}
  - \floatplacement{figure}{H}
  - \floatplacement{table}{H}
  - \usepackage{caption}
  - \usepackage{hyperref}
  - \usepackage[utf8]{inputenc}
  - \def\tightlist{}
---

>>>>

---
title: |
  Examining the Impact of School Closures on COVID-19 Infections in Europe and their Effects on Different Age Cohorts
author:
  - name: Damien Dupré
    affil: 1
    email: damien.dupre@dcu.ie (corresponding author)
  - name: Edgar Morgenroth
    affil: 1
    email: edgar.morgenroth@dcu.ie
affiliation:
  - num: 1
    address: |
      Dublin City University Business School, Glasnevin, Dublin 9, Ireland
thanks:
  author

@@

bibliography: bibliography.bib
abstract: |
  This paper analyzes the trends of COVID-19 cases in different age groups in selected European countries, assessing to what extent school closures helped reduce case numbers, how school closures affected case numbers in different age groups, and how COVID-19 spread between age groups. The study also evaluates the effects of school closures on COVID-19 cases using a Generalized Additive Model (GAM). The findings demonstrate a decreasing non-linear effect of school closure on the total COVID-19 case number across all countries studied. However, the analysis of age groups only reveals a consistent downward trend in infections in the 0 to 4 pre-school age group, while the school-going age groups 5 to 14 exhibit a significant increase in cases. Age groups 15 to 24 show a surge immediately after closure, followed by a decline. Transfer Entropy calculations highlight asymmetry in age group influences, indicating that changes in COVID-19 cases in certain age groups predict changes in other age groups but not vice versa. These findings contribute to a better understanding of COVID-19 dynamics in European countries and provide insights for public health strategies and interventions.
keywords: |
  COVID-19; School Closures; Intergenerational Transmission; Non-linear effects; Infection dynamics.
# \begin{jelcode}
# I18; C22.
# \end{jelcode}
output:
  bookdown::pdf_book:
    base_format: rticles::tf_article
    keep_tex: true
header-includes:
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{threeparttable}
  - \floatplacement{figure}{H}
  - \floatplacement{table}{H}
  - \usepackage{caption}
  - \usepackage{hyperref}
  - \usepackage[utf8]{inputenc}
  - \def\tightlist{}
---
